\sysfull

### 2018-08-05 paper/asplos19/intro.tex

\textbf{Challenges and Contributions.} This paper introduces \sys, a new task-based system that employs \emph{adaptive task size execution by task coalescing/splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks (Fig.~\ref{fig:coalesce}, top) or splits them (Fig.~\ref{fig:coalesce},bottom) based on the estimated energy availability without demanding any hardware support. \note{\textbf{To the best of our knowledge, \sys is the only task-based system that guarantees task termination and ....(something related with Coalescing...)  }}

The unique challenges and contributions revealed by this work are listed below:
\note{it takes more space, but a bullet list makes C1-C3 stand out more properly}

% \sys does not requires hardware support for energy estimation to make its scheduling decisions.

% \sys accepts any static decomposition and coalesces/splits its tasks at runtime. Two consecutive, coalesced tasks execute
% with no commit overhead between them, instead performing task-end commit actions at the end of the second task only.
% %
% When there is sufficient energy to execute both tasks, two distinct, small
% tasks are effectively executed as a single large task, preserving the atomicity
% of both. If power fails during a coalesced task, execution restarts from the
% {\em first} of the coalesced tasks. Figure~\ref{fig:coalesce} (top)
% illustrates how dynamic coalescing removes unnecessary overhead and shortens intermittent program execution.
% On the other hand, a large task that requires more energy to complete than a device buffered energy
% is split by \sys to enable task termination and preserve execution progress, as depicted in Figure~\ref{fig:coalesce} (bottom).

%\textbf{Challenges and Contributions}

\noindent \emph{C1) Task Transition Overhead:} given unpredictable incoming energy, how to save progress as few times as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.
% \noindent\emph{C1) Dynamic Task Sizing:} Given unpredictable energy shots arrival, how to specify the size of a dynamic task on the fly? \sys addresses this challenge by using a novel approach: \textit{recent execution history} as a metric to estimate the environment energy conditions and to specify task sizes. 
%Furthermore, It mitigates the risk of dynamic task re-execution by taking advantage of the certainty that the energy buffer offers and approaches the expected power interrupt carefully.

\noindent\emph{C2) Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rise to the need for dynamic memory consistency handling. How to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys does so by using a novel
approach called \emph{dynamic group privatization}--- %Varying variables dependencies forces a static approach (i.e.~\cite{alpaca}) to operate by considering a worst case scenario (i.e. protecting all global variables) in each dynamic task transition. 
performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).

\noindent\emph{C3) Ensuring Task Termination:} a static task decomposition model assumes that each
single task can execute to completion. If the hardware energy buffer provides
inadequate energy to execute each single task to completion, a program will not
terminate~\cite{cleancut_2018}. Under such conditions, how to enable the dynamic execution model to progress on a sub-task level? To avoid non-termination under adverse
energy conditions, \sys uses a novel timer-based {\em partial task commit} mechanism \note{should we instead cite Ratchet?}.
Partial execution avoids non-termination by committing the intermediate state of a long-running
task that has repeatedly failed and restarted.
%Partial execution violates task atomicity, but preserves forward progress; if a programmer knows that task atomicity is crucial to correctness, they can disable partial execution around a piece of code.

%\begin{itemize}
%\item\textit{challenge} 1) Given unpredictable energy shots arrival, how to specify the size of a dynamic task on the fly? \textit{contribution---1} \sys addresses this challenge by using its \textit{recent execution history} as a metric to estimate the environment energy conditions. Furthermore, It mitigates the risk of dynamic task re-execution by taking advantage of the certainty that the energy buffer offers and approaches the expected power interrupt carefully. 
%%
%\item\textit{challenge} 2) Given dynamic variables dependencies, how to ensure efficient data protection against power interrupts? \textit{contribution---2} \sys ensures the consistency of the data by using a novel
%approach called \emph{dynamic group privatization}. Varying variables dependencies forces a static approach (i.e.~\cite{alpaca}) to operate by considering a worst case scenario (i.e. protecting all global variables) in each dynamic task transition. \sys, therefore, utilizes a real-time data tracking to enable partial data protection on a task transition. Individual variables tacking, however, slows down a system dramatically. Therefore, \sys  relies on a coarse locality principle and protects the global variables in a batch. Moreover, it optimizes the data transfer by using Direct Memory Access (DMA).
%%
%\item\textit{challenge} 3) A static task decomposition model assumes that each
%single task can execute to completion. If the hardware energy buffer provides
%inadequate energy to execute each single task to completion, a program will not
%terminate~\cite{cleancut_2018}. under such conditions how to enable the dynamic execution model to progress on a sub-task level? \textit{contribution---3} To avoid non-termination under adversarial
%energy conditions, \sys uses a timer-based {\em partial task commit} mechanism.
%Partial execution avoids non-termination by committing the intermediate state of a long-running
%task that has repeatedly failed and restarted. Partial execution violates
%task atomicity, but preserves forward progress; if a programmer knows that
%task atomicity is crucial to correctness, they can disable partial execution around a piece of code.
%\end{itemize}
%

To asses the benefits of \sys over existing task-based systems, we implemented and tested six benchmarks on a real energy-harvesting platform. Our evaluation shows that \sys reduces run time by up to 54\%, and by 26\% on average, as compared to a state-of-the-art system, and is able to progress where static systems fail.

>>>>

\textbf{Challenges and Contributions.} This paper introduces \sys: a new task-based system that employs \emph{adaptive task size execution by task coalescing and splitting}. By means of this novel technique, small tasks can be executed efficiently by trimming unnecessary overheads \emph{dynamically}, meanwhile avoiding the risk of non-termination. \sys accepts any static decomposition and it coalesces (groups) tasks or splits them (see again Fig.~\ref{fig:coalesce}) based on the estimated energy availability without demanding any hardware support. To the best of our knowledge, \sys is the only task-based system that guarantees forward progress for any statically-defined tasks or energy storage sizes.

The unique contributions of \sys in relation to challenges of task-based systems revealed by this work are as follows:

\begin{itemize}

\item[C1] \emph{Overcoming Task Transition Overhead:} given unpredictable incoming energy, how to save computation progress as rare as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rise to the need for dynamic memory consistency handling. How to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys does so by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).

\item[C3] \emph{Ensuring Task Termination:} a static task decomposition model assumes that each single task can execute to completion. If the hardware energy buffer provides inadequate energy to execute each single task to completion, a program will not terminate~\cite{cleancut_2018}. Under such conditions, how to enable the dynamic execution model to progress on a sub-task level? To avoid non-termination under adverse energy conditions, \sys uses a novel timer-based {\em partial task commit} mechanism \note{should we instead cite Ratchet?}. Partial execution avoids non-termination by committing the intermediate state of a long-running task that has repeatedly failed and restarted.

\end{itemize}

To asses the benefits of \sys over existing task-based systems, we implemented and tested six benchmarks on a real energy-harvesting platform. Our evaluation shows that \sys reduces run time by up to 54\%, and by 26\% on average, as compared to a state-of-the-art system, and is able to progress where static task-based systems fail.
